Scikit-learn: machine learning without learning the machinery

### 2014-07-01 article.tex
rewrite feature hashing part
The output vectors of the feature hashing algorithm aren't really
hash tables; they are more similar to Bloom filters.

Dealing with a large corpus of text faces both challenges: many samples,
and a very high dimensional space. In addition, the dimensionality
tends to increase with sample size, as the number of different words used
is greater in large corpuses. Beyond the mere size of the data matrix
created by a standard vectorization approach, as above, another challenge
is that the vectorization must be done in two passes over the documents,
as the size of the output vector is not known before hand. Here, hashing,
a trick similar to random projection, can be used to tackle both of these
challenge and produce a streaming vectorizer, the {\tt HashingVectorizer}
in scikit-learn. The idea is to use a hash table, storing hashes of the
words, rather than the words themselves. The dimensionality of the hash
table is known from the hash size.

>>>>

Dealing with a large corpus of text faces both challenges: many samples,
and a very high dimensional space. In addition, the dimensionality
tends to increase with sample size, as the number of different words used
is greater in large corpuses. Beyond the mere size of the data matrix
created by a standard vectorization approach, as above, another challenge
is that the vectorization must be done in two passes over the documents,
as the size of the output vectors is not known beforehand.
Here, \emph{feature hashing} can be used
to tackle both of these challenges and produce a streaming vectorizer,
the {\tt HashingVectorizer} in scikit-learn.
The idea is to run words through a hash function, rather than a lookup table,
to map words to indices.
Collisions may occur, but the hashing algorithm \cite{weinberger2009}
is designed to mitigate their effect
(and because words often have multiple meanings,
``semantic'' collisions are inevitable in text processing tasks
\cite{attenberg2009}).
The dimensionality of the output vectors can be set by the user;
the bigger, the less likely collisions will occur.
